FAIR Theory: Applying Open Science Principles to the Construction and Iterative Improvement of Scientific Theories

### 2024-05-16 manuscript.Rmd
theories, frameworks, paradigms?!
Do we want to discuss this?

>>>>

In our experience, there is no clear delineation between paradigms, frameworks and theories. 
We think it is helpful to view these terms as discrete labels on a continuum from broad to narrow, from general to specific, when organizing knowledge.
Paradigms at the broadest level encompass the larger narrative, frameworks gather and organize concepts and terms, but only theories have a degree of specificity that allows us to derive specific testable and falsifiable hypotheses or models with exact mathematical relations between concepts (cf. Partelow, 2023, Table 1, https://link.springer.com/article/10.1007/s13412-023-00833-w#).
